The title

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
forgot to push from Caribou

*Method*

@@

*Participants*

@@

*Procedure*

@@

*Results*

@@

  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job). Figure ?? shows the distribution of the proportion of matches by person.

@@

```
```{r match percents by person}
#rc1 to rc 84

@@

*Discussion*

>>>>

# Method

@@

## Participants

@@

## Procedure

@@

# Results

@@

@@

## Alicia graphs

```{r matchpercentsbyperson}
#rc1 to rc 84

@@

  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job). Figure \@ref(fig:matchpercentsbyperson) shows the distribution of the proportion of matches by person.

## Kulas graphs

```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance."}

rc <- read.csv("resource_challenge.csv")
rh <- read.csv("resource_hind.csv")
ch <- read.csv("hind_challenge.csv")

rc$type <- "Resource-Challenge"
rh$type <- "Resource-Hindrance"
ch$type <- "Challenge-Hindrance"

forgraph <- rbind(rc,rh,ch)

library(ggplot2)

#ggplot(forgraph, aes(x = mean, fill = type)) +
#  geom_density(alpha = .3) +
#  xlab("Percent Agreement") + labs(fill = "Att/Engage\nInteraction")

p <- ggplot(forgraph, aes(x = mean)) + geom_histogram()
p + facet_wrap(~type, nrow=3)

## lotsa variance in resource-challenge agreement. Next look for either content (O*Net category) or contextual (job) moderator

Figure \@ref(fig:percagree) shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources or as challenges and hindrances. Alternatively, whether a characteristic was viewed as both a resource and a challenge had quite a bit of variability.

```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales)."}

rc$scale <- c(rep("Structural",10), rep("Physical", 20), rep("Interpersonal",13), rep("Information Input", 5), rep("Mental Processes", 10), rep("Work Output", 9), rep("Interact with Others", 17))

ggplot(rc, aes(x=mean)) + geom_histogram() + facet_wrap(~scale, nrow=7)

#ggplot(rc, aes(x = mean, fill = scale)) +
#  geom_density(alpha = .3) +
#  xlab("Percent Agreement") + labs(fill = "ONET grouping")

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. We categorized each characteristic by its ONet "scale" (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other *types* of characteristics (for example, "Physical" characteristics).

>Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).

# Discussion

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.tex
forgot to push from Caribou

\emph{Method}

@@

\emph{Participants}

@@

\emph{Procedure}

@@

\emph{Results}

@@

Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.
In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.

@@

>>>>

\hypertarget{method}{%
\section{Method}\label{method}}

@@

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.

In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.

@@

\hypertarget{alicia-graphs}{%
\subsection{Alicia graphs}\label{alicia-graphs}}

\begin{verbatim}
## [1] 0.1830986 0.6231884 0.4528302 0.2068966 0.6415094 0.6666667
\end{verbatim}

\includegraphics{Submission_ResourceCount_files/figure-latex/matchpercentsbyperson-1.pdf}

To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job). Figure \ref{fig:matchpercentsbyperson} shows the distribution of the proportion of matches by person.

\hypertarget{kulas-graphs}{%
\subsection{Kulas graphs}\label{kulas-graphs}}

\begin{figure}
\centering
\includegraphics{Submission_ResourceCount_files/figure-latex/percagree-1.pdf}
\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.}
\end{figure}

Figure \ref{fig:percagree} shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources or as challenges and hindrances. Alternatively, whether a characteristic was viewed as both a resource and a challenge had quite a bit of variability.

\begin{figure}
\centering
\includegraphics{Submission_ResourceCount_files/figure-latex/recchall-1.pdf}
\caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
\end{figure}

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. We categorized each characteristic by its ONet ``scale'' (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other \emph{types} of characteristics (for example, ``Physical'' characteristics).

\begin{quote}
Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).
\end{quote}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout. Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work. The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a). Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement. While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless. The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes. It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
Further, total resources were highly associated challenge demands (supporting H4). We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86). Need to also talk about our exploratory findings regarding patterns across job type
Limitations and Future Directions
As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future. First, while a strength of this project, arguably, is the use of O\emph{Net items, practical considerations limited the number of job characteristics we could include in our survey. Future study could consider additional or other O}Net items. We conceptualized resources and demands in terms of perceived total amounts. It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically. Further, our study was limited to three outcomes of interest. It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
